### 2021-02-12 Modules/paper_sec_prlms.tex
Sent as draft No.2

\section{Beamforming}\label{sec:setup}
In this section, a brief overview on ULA beamforming and its resemblance to FIR filter design are presented.
Consider an $N$-element ULA with inter-element spacing $\delta$, where its $n$'th sensor is positioned at $\vpi{n},\;\text{for}\; n=0,\ldots,N-1$. We set $\vpi{0}$ as the axis reference point and assume that the target of interest is positioned at $\vpt$.
Focusing on a far field localization problem, DOA and target range are to be estimated. Without loss of generality, aiming to simplify the exposition, we assume $2\text{D}$ planar problem, where DOA is described by a single angle $\thetaD$, measured from the array's broadside.
For simplicity, we assume an anechoic environment, an array of identical omni-directional sensors and a stationary target of interest.
Inspired by radar based applications, we also place a transmitter at $\vpi{0}$, assuming the transmitted signal $s$, is reflected back from the target and re-impinges the array, with a total time delay of $\tau_{\text{pd}}=2R/c$ seconds, where $R = \norm{\vpt-\vpi{0}}$ is the target's range and $c$ represents the propagation velocity of the signal in the medium.
In this work, we use the following conventions; vectors and matrices are denoted by lower and upper case bold italic letters respectively. 
$v_{i}$ and $A_{ij}$ are the $i$-th element of the vector $\vecnot{v}$ and the $i,j$-th element of the matrix $\vecnot{A}$.
Also, $\vecnot{A}^{T}$, $\vecnot{A}^{*}$ and $\vecnot{A}^{H}$ are the transpose, conjugate and Hermitian transpose of the matrix $\vecnot{A}$ respectively.
\par Let $x_{n}(t)$ be the measured signal at the $n$'th sensor
x_{n}(t) = gs\Brack{t-\tau_{pd}-\tau_{n}},
\label{eqn:noFeedbackULA_singleSensor_temporal}
where $\tau_{n}=n\delta\cos\Brack{\thetaD}/c$ represents the time difference of arrival between the $n$'th sensor and the reference sensor and $g$, being a scalar in an anechoic environment, is the channel's gain, related to both propagation and the target's radar cross section (RCS).
Defining $\vecnot{x}\rBrace{t}\triangleq\vBrace{x_{0}\rBrace{t}\hdots{}x_{N-1}\rBrace{t}}^{T}$ and its Fourier transform, $\vecnot{\F{x}}\rBrace{\omega}\triangleq\vBrace{X_{0}\rBrace{\omega},\hdots,X_{N-1}\rBrace{\omega}}^{T}$, one may write 
\[
\vecnot{\F{x}}\rBrace{\omega}=g\vecnot{d}\rBrace{\omega}\F{s}\rBrace{\omega}\exp{\rBrace{-j\omega\tau_{pd}}}
\]
where $S\rBrace{\omega}$ is the Fourier transform of $s\rBrace{t}$ and $\vdO$ denotes the steering vector whose $n$'th element is
    \label{eq:d}
    d_{n}\rBrace{\omega} = \exp{\rBrace{-j\omega\tau_{n}}}.
Denoting the beamformer's weights as $\vBeta\rBrace{\omega}$ and the beamformer's output as $z$, we express the latter in the frequency domain
    \label{eq_Z}
    Z\rBrace{\omega} = g\vecnot{\beta}^{H}\rBrace{\omega}\vecnot{d}\rBrace{\omega}\F{s}\rBrace{\omega}\exp{\rBrace{-j\omega\tau_{pd}}}.
Defining the electric phase to be
\begin{equation}\label{eq:thetaULA}
\theta=\omega{\delta\cos\Brack{\thetaD}}/{c},
we rewrite \eqref{eq_Z} as 
\[
Z\rBrace{\omega} = g\F{s}\rBrace{\omega}\exp{\rBrace{-j\omega\tau_{pd}}}\sum_{n=0}^{N-1}\beta^{*}_{n}\rBrace{\omega}\exp\Brack{-jn\theta},
\]
hence in the ULA case, aiming for a desired spatial response, the weights vector $\vecnot{\beta}\rBrace{\omega}$ configuration is mathematically equivalent to an FIR filter design~\cite{van1988beamforming,benesty2018}. 
Assuming narrowband stimuli signals, we suppress $\omega$ dependency in the notation throughout the rest of this paper, where possible.
\par In standard radar signal processing schemes, a waveform is transmitted to, and reflected from the target of interest. Then, the reflected signal is processed by the radar reception array in order to estimate the target's dynamics (e.g., DOA, range, velocity etc.). 
As opposed to the standard scheme, we suggest a continuous re-transmission of the signal and its echoes back to the platform, generating a spatial feedback loop between the array and the target.
Another deviation from traditional radar processing, used to simplify the exposition, is using continuous-wave (CW) stimuli, rather than using pulse based signals. 
% The suggested structure is elaborated in Sec.~\ref{sec_introduceFeedback} and shown to be equivalent to IIR filter design.
\section{Feedback Beamforming}

@@

Inspired by time domain ``Direct form II'' IIR filter design (see Fig.~\ref{fig_IIRBasicArch}), 

@@

        \begin{overpic}[width=0.7\linewidth, 
        tics=10,trim=0 0 0 0]{./Media/BASIC_IIR_FILTER_ARCH.png}
            \put (60, 50){\footnotesize{$\beta_{0}$}}
            \put (60, 30){\footnotesize{$\beta_{1}$}}
            \put (60, 10){\footnotesize{$\beta_{2}$}}
            \put (36, 30){\footnotesize{$\alpha_{1}$}}
            \put (36, 10){\footnotesize{$\alpha_{2}$}}
            \put (10, 50){\footnotesize{$x$}}
            \put (85, 50){\footnotesize{$y$}}
            \put (47.5, 34.5){\footnotesize{$z^{-1}$}}
            \put (47.5, 14.5){\footnotesize{$z^{-1}$}}
    \caption{Direct form II $2^{nd}$ order IIR architecture.}
    \label{fig_IIRBasicArch}

@@

        \begin{overpic}[width=0.95\linewidth, 

@@

\subsection*{Obtained spatial response}

@@

@@

In this section we analyze the suggested FB (see Fig.~\ref{fig:Proposed_spatialIIR_ARCH}), considering some fundamental properties which are commonly used to asses array performance: Beamwidth, peak-to-sidelobe level, and directivity. Each property is then compared to traditional passive ULAs, showing that significantly improved performances are obtainable with spatial feedback integration.  
\subsection*{Error terms}
In the absence of accurately known parameters, we denote $\hat{\phi},\hat{\theta}$ to be the range and DOA related phase estimates respectively.
Then, using the same weights as in \eqref{eq:alpha_beta_opt} for both the feedback and output synthesis gives rise to
\begin{equation}\label{eq:alpha_beta_hat}
\vBetaCFB=\vAlphaCFB=\frac{\vdHatC\exp\rBrace{j\hat{\phi}}}{\hat{g}\norm{\vdHat}^2},
introducing the estimated steering vector 
\begin{equation}\label{eq:d_hat}
\vdHat=\vBrace{1,\exp(-\hat\theta),\ldots,\exp(-(N-1)\hat\theta)}^T.
Plugging \eqref{eq:alpha_beta_hat} into \eqref{eqn:GeneralFeedbackTransferFunction}, results in
\begin{equation}\label{eq:SF_CB}
    \resizebox{.894\linewidth}{!}{
            \HbaFB=\frac{r\D{\dTheta/2}{N}\exp\rBrace{-j\rBrace{\dPhi+(N-1)\dTheta/2}}}{1-r\D{\dTheta/2}{N}\exp\rBrace{-j\rBrace{\dPhi+(N-1)\dTheta/2}}}
where \[
\D{x}{N}\triangleq\frac{1}{N}\frac{\sin\rBrace{Nx}}{\sin\rBrace{x}}
\]
is the normalized Dirichlet kernel and
\[
\dTheta\triangleq\theta-\hat{\theta},\ \dPhi\triangleq\phi-\hat{\phi},\ 
r\triangleq g/\hat{g},
\]
are defined as the DOA, range and gain error terms respectively.
In the following, four fundamental scenarios are considered:
\begin{itemize}
    \item{\makebox[.35\linewidth]{Perfect alignment \hfill} $\rBrace{\dTheta=0\ , \dPhi=0},$}
    \item{\makebox[.35\linewidth]{Steering error \hfill} $\rBrace{\abs{\dTheta}>0\ , \dPhi=0},$}
    \item{\makebox[.35\linewidth]{Range error \hfill} $\rBrace{\dTheta=0\ , \abs{\dPhi}>0},$}
    \item{\makebox[.35\linewidth]{General \hfill} $\rBrace{\abs{\dTheta}>0\ , \abs{\dPhi}>0}.$}
\end{itemize}
\ifdefined\showTodo
    \subsection*{Small estimation error analysis - \textbf{TO BE REMOVED - kept only for the todos}}
    \label{subsection_ArrayPerformance_TayolrAnalysis}
    \myTodo{inline}{\textbf{DONE:}\\ maybe to call this subsection 'small error analysis'}
    Plugging (\ref{eqn_CB_coefSet}) into (\ref{eqn:GeneralFeedbackTransferFunction}) and denoting $\D{N}{x} \triangleq \frac{\sin{\rBrace{Nx}}}{\sin{\rBrace{x}}}$ results in the general \coefSetName{} beampattern \myTodo{inline}{\textbf{DONE}\\you need to define the delta expressions (the errors)}
        h_{\coefSetName{}}\rBrace{\theta,\omega}
        \D{N}{\dTheta/2}exp\rBrace{-j\rBrace{\dPhi+\frac{N-1}{2}\dTheta}}
        N - \D{N}{\dTheta/2}exp\rBrace{-j\rBrace{\dPhi+\frac{N-1}{2}\dTheta}}
    For the evaluation of the various array parameters, we define the normalized beampattern \myTodo{inline}{\textbf{DONE:}\\not very readable. Consider writing a multiplication of two terms. Suggesting that you write the expression in eq(5) as $H(\theta,\phi)$ and here you'll have $H(\hat{\theta}, \hat{\phi})/ H(\theta,\phi)$}
        \label{eqn_arrPerformance_beamwidth_3dB}
        \Hr{\theta}{\tau}{}\triangleq\fbBpRatio.
    \myTodo{inline}{\textbf{DONE:}\\this next section is very long. Suggesting that you express (10) in terms of the errors $\Delta\theta,\;\Delta\phi$, and then simply state that the second order Taylor expansion of those errors around zero gives (12). One more issue which I think might cause us some headache is that we cannot assure that $\Delta\phi$ (you call it $\Delta\tau$) is indeed close to zero, as this term fluctuates very fast. But we will think about it later on. Maybe something with wideband signal stimulus will solve this issue.}
    The pursuit for analytic dependencies between $\Hr{\theta}{\tau}{}$, $\dTheta$ and $\dPhi$, as in \cite{van2004optimum}, lead to expressing $\Hr{\theta}{\tau}{}$'s multivariate Taylor expansion, setting $\dTheta,\dPhi$ as the variables. Simulations have shown that $2^{nd}$ Taylor expansion achieves very accurate results, thus we use it to express the array parameters. As commonly known, the Taylor expansion of a multivariate analyzable function $f\rBrace{\vx}$ around $\vx_{0}$ where $\vx \in \mathbb{R}_{M\times1},$ is 
        \label{eqn_h_Tylor_dTheta_dTau}
        \evalat{f\rBrace{\vx}}{\vx\to\vx_{0}}=\sum_{n=0}^{\infty}\frac{1}{n!}\rBrace{\sum_{i=1}^{M}(x_{i}-x_{0i})\frac {\partial}{\partial x_i} }^n f(x_k)|_{x_k=x_{k0}},
    where $\frac{\partial}{\partial x_i}$ is the derivative operator and $i\in\left[1\hdots{}M\right]$. Reducing (\ref{eqn_h_Tylor_dTheta_dTau}) to its $2^{nd}$ form (i.e $f(x,y)=\sum_{n=0}^{\infty} \frac 1 {n!}\rBrace{x\frac {\partial}{\partial x}+y\frac {\partial}{\partial y} }^n f(x,y)|_{(x,y)=(0,0)}$), combined with the binomial formula, $(x+y)^{n}=\sum _{k=0}^{n}{\binom {n}{k}}x^{n-k}y^{k},$ multiple iterations of L'Hôpital's rule and algebraic simplification finally yields
            \evalat{\Hr{\theta}{\tau}{}_{\coefSetName{}}}{\dTheta\to0,\dPhi\to0} \approx\ & 1 
            \\+&\frac{\binom{2}{0}}{2!}\frac{-\rBrace{N - 1}\rBrace{N-4r+2Nr+1}}{6\rBrace{r-1}^{2}}\dTheta^{2}
            \\+&\frac{\binom{2}{1}}{2!}\frac{-r\omega\rBrace{N - 1}}{\rBrace{r-1}^{2}}\dTheta\dPhi
            \\+&\frac{\binom{2}{2}}{2!}\frac{-2r\omega^{2}}{\rBrace{r-1}^{2}}\dPhi^{2}
\subsection*{The normalized beampattern}

@@

As commonly done for ULA performance analysis \cite{van2004optimum}, we analyze the normalized response (i.e., where the peak main lobe gain is set to $0_{dB}$). Henceforth, setting $\vecnot{\beta}_{\coefSetName,\text{opt}}=\vecnot{\alpha}_{\coefSetName,\text{opt}},$ we define the normalized response

@@

    \resizebox{0.89\linewidth}{!}{

@@

\vfill
\subsection*{Half power beamwidth}
\input{./Modules/arrayPerformance_beamwidth.tex}
\subsection*{Sidelobes attenuation}

@@

\subsection*{Array directivity}
The array directivity $\mathcal{D}$ \cite{van2004optimum}, defined as

@@

measures the ratio between the maximal array gain at its mainlobe, to the average gain over all directions. 
For uniformly weighted ULAs with no feedback, it is known \cite{van2004optimum} that $\mathcal{D}\rBrace{N,0} = N$.
Plugging \eqref{eq_Hdphi0} within \eqref{eq_D} and by numerical evaluation (see Fig.~\ref{fig_directivity}) we suggest to approximate the directivity with 

@@

     \caption{Plot of $\mathcal{D}\rBrace{N,r}$, computed using numerical integration (surface), shown to perfectly match the analytic expression (black diamonds) presented in \eqref{eq_D_result}. Difference between the numerical integration result and the suggested analytic expression is around $\sim{1e^{-9}}$.}

@@

\subsection*{Summary}
To conclude this section, we summarize the feedback integration related performance improvements in Table.~\ref{table_arrayPerformance} 

@@

    \resizebox{1\linewidth}{!}{

@@

>>>>

In this chapter, we revisit the most basic DOA estimation approach, i.e. beamforming, and present our novel feedback based architecture.
The feedback based beamforming concept is introduced in Sec.~\ref{sec_introduceFeedback}.
Then, we apply information theory related reasoning for the array setting in Sec.~\ref{sec_FIM}, namely we use the Fisher Information Matrix.
The resultant beamformer's temporal response and spatial performance are analysed in Sec.~\ref{sec_stability} and Sec.~\ref{sec_Performance} respectively, assuming ideal noiseless scenario.
Considering practical scenarios, the beamformer's noise sensitivity is exemplified in Sec.\ref{sec_sim}, followed by a practical and robust dual-frequency beamformer which is presented in Sec.~\ref{sec_app}.

\section{Notations and problem setup}

@@

Inspired by time domain ``Direct form II'' IIR filter design (see Fig.~\ref{fig_IIR_arch}), 

@@

@@

        \begin{overpic}[width=0.5\linewidth, 

@@

\subsection{Obtained spatial response}

@@

\section{Temporal Stability}
\label{sec_stability}
\input{./Modules/sec_stability.tex}

@@

In this section we analyze the suggested FB (see Fig.~\ref{fig:Proposed_spatialIIR_ARCH}), considering some fundamental properties which are commonly used to asses array performance and discussed in Sec.~\ref{sec:prlm_array_perf}: Beamwidth, peak-to-sidelobe level, and directivity. Each property is then compared to traditional passive ULAs, showing that significantly improved performances are obtainable with spatial feedback integration.
\subsection{The normalized beampattern}

@@

Applying the \emph{normalized beampattern} concept of Sec.~\ref{sec:prlm_array_perf} to this work, we set $\vecnot{\beta}_{\coefSetName,\text{opt}}=\vecnot{\alpha}_{\coefSetName,\text{opt}},$ giving rise to

@@

    %\resizebox{0.89\linewidth}{!}

@@

\subsection{Half power beamwidth}
\input{./Modules/arrayPerformance_beamwidth_LOCAL.tex}
\subsection{Sidelobes attenuation}

@@

\subsection{Array directivity}
In the context of this work, the directivity is expressed as

@@

Plugging \eqref{eq_Hdphi0} within \eqref{eq_D} and by numerical evaluation (see App.~\ref{apndx_directivityFit} and the complementary Fig.~\ref{fig_directivity}) we suggest to approximate the directivity with 

@@

     \caption{Plot of $\mathcal{D}\rBrace{N,r}$, computed using numerical integration (surface), shown to perfectly match the analytic expression (black diamonds) presented in \eqref{eq_D_result}.}

@@

\subsection{Summary}
To conclude this section, we summarize the feedback integration related performance improvements in Table.~\ref{table_arrayPerformance}.

@@

    %\resizebox{1\linewidth}{!}

@@

Also, in Fig.~\ref{fig_perf} we demonstrate the HPBW and sidelobe attenuation for 3 elements ULA.
As the expressions for HPBW and sidelobe-attenuation are relevant for $\sim{}N>20$, we also simulate 20 elements ULA for in Fig.~\ref{fig_perf20}. 
In Table.~\ref{table_arrayPerfEmp} we show the coherency between the results and the performance related expressions of Table.~\ref{table_arrayPerformance}.
As predicted, the results of Fig.~\ref{fig_perf20} are consistent with the theoretical expressions.
        \begin{overpic}[width=0.9\linewidth, 
        tics=10,trim=0 0 0 0]{./Media/fig_performance.png}
            \put (9, 36.5){$dB$}
            \put (2, 20){$\abs{H}^{2}$}
            \put (27, 0){$\theta_{d}/\pi$}
            \put (34.5, 67){$r=0$}
            \put (29, 63){\rotatebox{-90}{\tiny{HPBW = $0.1\pi$}}}
            \put (40, 61){\tiny{$-19.08_{dB}$}}
            \put (77.5, 67){$r=0.3$}
            \put (73.14, 63){\rotatebox{-90}{\tiny{HPBW = $0.073\pi$}}}
            \put (83.5, 58.5){\tiny{$-23.43_{dB}$}}
            \put (34.5, 31.5){$r=0.6$}
            \put (29, 27){\rotatebox{-90}{\tiny{HPBW = $0.043\pi$}}}
            \put (40, 18.75){\tiny{$-31.09_{dB}$}}
            \put (77.5, 31.5){$r=0.8$}
            \put (73.14, 27){\rotatebox{-90}{\tiny{HPBW = $0.02\pi$}}}
            \put (84.25, 13.5){\tiny{$-41.6_{dB}$}}
     \caption{Simulating 3 elements ULA based feedback beamformer for $r$ values of 0, 0.3, 0.6 and 0.8.
     The HPBW is marked with vertical red dashed line, where an auxiliary horizontal line of $\abs{H}^{2} = 1/2$ is also provided.
     The sidelobe attenuation is cited in each plot in a textual fashion.}
    \label{fig_perf}
        \begin{overpic}[width=0.9\linewidth, 
        tics=10,trim=0 0 0 0]{./Media/fig_performance20.png}
            \put (9, 36.5){$dB$}
            \put (-3, 20){$\abs{H}^{2}$}
            \put (27, 0){$\theta_{d}/\pi$}
            \put (34.5, 67){$r=0$}
            \put (29, 63){\rotatebox{-90}{\tiny{HPBW = $0.0605\pi$}}}
            \put (32.25, 56.5){\tiny{$-26.38_{dB}$}}
            \put (77.5, 67){$r=0.3$}
            \put (73, 63){\rotatebox{-90}{\tiny{HPBW = $0.0454\pi$}}}
            \put (79, 53.75){\tiny{$-32.06_{dB}$}}
            \put (34.5, 31.25){$r=0.6$}
            \put (29, 27){\rotatebox{-90}{\tiny{HPBW = $0.0259\pi$}}}
            \put (40, 14){\tiny{$-41.21_{dB}$}}
            \put (77.5, 31.25){$r=0.8$}
            \put (73, 27){\rotatebox{-90}{\tiny{HPBW = $0.0127\pi$}}}
            \put (84.25, 12.5){\tiny{$-52.55_{dB}$}}
     \caption{Simulating 20 elements ULA for the sake of HPBW analysis.
     As in Fig.~\ref{fig_perf}, $r$ values of 0, 0.3, 0.6 and 0.8 are simulated.
     The HPBW is marked in the same manner also.}
    \label{fig_perf20}
    \caption{Performances of conventional beamformer $r=0$ and the proposed Feedback-Beamforming Architecture, for several $r$ values.
    Also comparison to expected theoretical expressions is provided.}
    %\resizebox{1\linewidth}{!}
        \begin{tabular}{||c | c c c | c c c||}
            & \multicolumn{3}{c|}{HPBW [RAD]} & \multicolumn{3}{c||}{SIDELOBE GAIN [dB]} \\ [0.5ex]
            Expected & \multicolumn{3}{c|}{$\frac{\rBrace{1-r}\rBrace{-0.4r+1.4}}{1.4}$} & \multicolumn{3}{c||}{$20\log{}\rBrace{\abs{\frac{2\rBrace{1-r}}{3\pi}}^{2}}$} \\ [0.5ex]
            & Result & Expected & Error & Result & Expected & Error \\ [0.5ex] 
            $r=0$ & 0.0605 & 0.07 & 0.0095 & -26.38 & -26.93 & 0.55 \\ [0.5ex]
            $r=0.3$ & 0.0454 & 0.0448 & 0.006 & -32.06 & -33.12 & 1.06 \\ [0.5ex]
            $r=0.6$ & 0.0259 & 0.0232 & 0.0027 & -41.21 & -42.84 & 1.63 \\ [0.5ex]
            $r=0.8$ & 0.0127 & 0.0108 & 0.0019 & -52.55 & -54.88 & 2.33 \\ [0.5ex]
    \label{table_arrayPerfEmp}

### 2021-02-12 Modules/sec_conclusions_LOCAL.tex
Sent as draft No.2

Integrating feedback into standard beamformers proved to achieve the spatial domain equivalent of the temporal IIR filtering.
It seems that a simple generalization of the conventional-beamformer maximizes (locally) the system's spatial information, thus enabling high localization accuracy.
The feedback-based architecture performance evaluation predicts an unlimited improvement in all criteria, when considering perfect knowledge of the target's range and the channel attenuation.
It turns out that a single frequency waveform based feedback-beamformer is impractical, being too sensitive to even mild target range estimation errors.
Fortunately, using a dual-frequency waveform and applying simple frequency domain manipulations to the output and feedback signals, were found to serve as a low frequency (hence low sensitivity) equivalent of the single frequency scheme.
Also, the dual frequency scheme proved to be of low noise sensitivity, featuring high performance even in relatively low signal-to-noise-ratio scenarios.
\par Future study of the feedback beamforming concept may be applied to other array processing applications other than localization.
Furthermore, it is worthwhile to inspect other interesting choices of coefficients rather than the conventional-beamformer generalization, other waveforms and associated processing schemes, to extend the results to dynamic/multiple targets and to consider sensors with general radiation patterns.
Also, one may consider generalizing the suggested architecture to multiple-input-multiple-output systems, enabling a steered/focused (rather than omni-directional) feedback transmission.

>>>>

Integrating feedback into standard beamformers proved to achieve the spatial domain equivalent of the temporal IIR filtering.
It seems that a simple generalization of the conventional-beamformer maximizes (locally) the system's spatial information, thus enabling high localization accuracy.
The feedback-based architecture performance evaluation predicts an unlimited improvement in all criteria, when considering perfect knowledge of the target's range and the channel attenuation.
It turns out that a single frequency waveform based feedback-beamformer is impractical, being too sensitive to even mild target range estimation errors.
Fortunately, using a dual-frequency waveform and applying simple frequency domain manipulations to the output and feedback signals, were found to serve as a low frequency (hence low sensitivity) equivalent of the single frequency scheme.
Also, the dual frequency scheme proved to be of low noise sensitivity, featuring high performance even in relatively low signal-to-noise-ratio scenarios.
\par In the following, we overview some interesting leads for future study of the feedback beamforming concept.

### 2021-02-12 Modules/sec_future_dynamic.tex
Sent as draft No.2

Revisiting \eqref{eqn:SingleSensorTemporalEquality}, a natural initial generalization would be to allow the target of interest to be dynamic, i.e. introducing a general 2D arbitrary target location $\vecnot{p}_{t}\rBrace{t}$.
The location dynamics may be translated into a dynamic propagation delay, $\tau_{pd}\rBrace{t}$.
It follows that an auxiliary temporal quantity should be defined, $t_{i}\rBrace{t}$, which links between the received signal's impinging moment $t$, and its corresponding reflecting moment in the target of interest.
Hence one may describe it as
\begin{equation}
    t_{i}\rBrace{t}=\underset{\tau}{\mathrm{arg}}\cBrace{\tau-t=\frac{R\rBrace{\tau}}{c}}.
\end{equation}
With $t_{i}$, we rewrite \eqref{eqn:SingleSensorTemporalEquality} as
\begin{equation}
    \label{eqn:ftr_dyn_temp}
    x_{n}(t) = g\rBrace{s\rBrace{t_{i}\rBrace{t}}
    +\sum_{m=0}^{N-1}{\alpha^{*}_{m}x_{m}\rBrace{t_{i}\rBrace{t}}}}.
\end{equation}
One may consider the following research approaches for further investigation
\begin{itemize}
    \item \textbf{Modeling of target's location}
    \\Considering a constant velocity $\vecnot{v}_{\theta,\phi}$, of the target, where $v_{\theta}$ and $v_{\phi}$ are the radial and the tangent velocity components respectively, will result in a closed form expression for $t_{i}$, $$t_{i}=\frac{R_{0}+\rBrace{c+v_{\theta}}t}{c}$$, where $R_{0}$ and further development may lead to a closed form response like in the stationary case.
    In this manner, other component may be added to the positional equation.
    \item \textbf{Frame based processing}
    \\Considering low velocity of the target with respect to the wave's propagation's speed, one may consider treating the processor as pseudo-stationary and explore its implications for increasing velocities/processing duration. 
\end{itemize}

>>>>

Revisiting \eqref{eqn:SingleSensorTemporalEquality}, a natural initial generalization would be to allow the target of interest to be dynamic, i.e. introducing a general 2D arbitrary target location $\vecnot{p}_{t}\rBrace{t}$.
The location dynamics may be translated into a dynamic propagation delay, $\tau_{pd}\rBrace{t}$.
It follows that an auxiliary temporal quantity should be defined, which for a given impinging signal, expresses it's transmission time. 
Hence, we denote the moment of transmission $t_{i}\rBrace{t}$ as
\begin{equation}
    % t_{i}\rBrace{t}=\underset{\tau}{\mathrm{argmin}}\cBrace{\tau=\frac{R\rBrace{\tau}}{c}}.
    t_{i}\rBrace{t} = \cBrace{t - 2\tau\ \middle\vert\ t - \tau = \frac{R\rBrace{t-\tau}}{c}}
\end{equation}
With $t_{i}$, we rewrite \eqref{eqn:SingleSensorTemporalEquality} as
\begin{equation}
    \label{eqn:ftr_dyn_temp}
    x_{n}(t) = g\rBrace{s\rBrace{t_{i}\rBrace{t}}
    +\sum_{m=0}^{N-1}{\alpha^{*}_{m}x_{m}\rBrace{t_{i}\rBrace{t}}}}.
\end{equation}
One may consider the following research approaches for further investigation
\begin{itemize}
    \item \textbf{Modeling of target's location}
    \\Considering a constant velocity $\vecnot{v}_{\theta,\phi}$, of the target, where $v_{\theta}$ and $v_{\phi}$ are the radial and the tangent velocity components respectively, will result in a closed form expression for $t_{i}$, $$t_{i}=\frac{R\rBrace{t=0}+\rBrace{c+v_{\theta}}t}{c},$$ where $R\rBrace{t=0}$ is the initial distance to the target of interest and further development may lead to a closed form response like in the stationary case.
    In this manner, other components may be added to the positional equation.
    \item \textbf{Frame based processing}
    \\Considering low velocity of the target with respect to the wave's propagation's speed, one may consider treating the processor as pseudo-stationary and explore its implications for increasing velocities/processing duration. 
\end{itemize}

### 2021-02-12 Modules/sec_future_wavfrom.tex
Sent as draft No.2

In practical RADAR related systems, the waveform of choice is pulse (chirp) based.
It holds some obvious advantages over the CW transmission such as
\begin{itemize}
    \item Lower power consumption
    \item Inherent nulling in the radial axis (localization)
    \item Possible match filters should allow the decision of weather to re-transmit or not
    \item In multi target scenario, there is a smaller chance of interference.
    \item The most interesting research option is the use of several (possibly many) independent harmonics as super positioned multiple dual frequency beamformers, which simultaneously scan a wide area with multiple resolutions, by merely selecting harmonic couples and filter coefficients, where each harmonic/coefficient set it pointed to a specific area.
    In the expense of computational effort (without adding elements to the array), it seems possible that one may have simultaneous scan of the entire arena in any wanted direction/range/resolution.
\end{itemize}

>>>>

In practical RADAR related systems, the waveform of choice is pulse (chirp) based.
It holds some obvious advantages over the CW transmission such as
\begin{itemize}
    \item Lower power consumption
    \item Possible match filters should allow the decision of weather to re-transmit or not
    \item In multi target scenario, there is a smaller chance of interference.
    \item The most interesting research option is the use of several (possibly many) independent harmonics as super positioned multiple dual frequency beamformers, which simultaneously scan a wide area with multiple resolutions, by merely selecting harmonic couples and filter coefficients, where each harmonic/coefficient set it pointed to a specific area.
    In the expense of computational effort (without adding elements to the array), it seems possible that one may have simultaneous scan of the entire arena in any wanted direction/range/resolution by mere choosing multiple frequency couples which are simultaneously processed independently.
    \par 
    As a simple example, consider that the arena consists of $M$ zones of interest, where each zone may be described as a angular bounded radial slice (similar to the visualization of Fig.~\ref{fig_rangeAzimuthSelectivity}) which may be described as $$a_{m}=\cBrace{\vecnot{p}\ \middle\vert\  \theta_{d,m,\text{min}}<\text{DOA}\rBrace{\vecnot{p}}<\theta_{d,m,\text{max}}\ ,\ R_{m,\text{min}}<\norm{\vecnot{p}}<R_{m,\text{max}}}\ \forall\ m=0\dots{}M-1.$$
    \par
    Each zone will be assigned with matching couple of carrier frequencies ($\omega_{1,2}$) to cover its radial width (where the radial width is equivalent to $R_{\text{rt}}$ of \eqref{eq_DF_phErr}) and coefficient sets ($\vecnot{\alpha}_{m,i},\vecnot{\beta}_{m,i} \ \forall\ m=0\dots{}M-1, i=1,2$), which cover the zone's angular diameter which is equivalent to determining the desired beamwidth via setting the proper $\kappa$ of \eqref{eqn_H_DF_CB}.
    \par
    Leaving aside the needed computational effort and physical limitations of transmitting multiple narrowband signals, assuming large $M$ values, we have a super-positioned feedback beamformer which simultaneously scans the entire arena.
\end{itemize}
